On Extensibility and Personalizability of Multi-Modal Trip Planning

### 2016-03-03 paper.tex
Updated section Results.

The user-created data are the auxiliary data that is represented as pairs
of latitude and longitude degrees.
To merge these lat-long pairs into the planner, we performed a neighborhood
search to calculate the total score of auxiliary data for each 
lat-long pair already in our planner.
It might be of strong interest to some user for our planning
system to take care of criminal statistics so that some level of safety
of the resulting routes is guaranteed.
For instance, a user traveling through the downtown area of San Francisco
around midnight may want to upload a data set of crimes (cf. \figref{sf_crime}), 
and express her constraints and preferences in hope of a preferred trip plan.

@@

\subsection{System Architecture}
\begin{figure*}[!ht]
  \centering
    \includegraphics[width=0.8\textwidth]{figs/system.pdf}
  \caption{System Overview\label{fig:system}}
\end{figure*}
We designed and implemented a multi-modal trip planning
system based on a high-performance graph search engine.
The planner allows user uploads, as well as declarative
constraints and preferences.
We now describe the structure of the planning system.

@@

Our agent needs to commute back home at night.

>>>>

The user-created data are the auxiliary data that is represented as pairs
of latitude and longitude degrees.
To merge these lat-long pairs into the planner, we performed a neighborhood
search to calculate the total score of auxiliary data for each 
lat-long pair already in our planner.
It might be of strong interest to some user for our planning
system to take care of criminal statistics so that some level of safety
of the resulting routes is guaranteed.
For instance, a user traveling through the downtown area of San Francisco
around midnight may want to upload a data set of crimes (cf. \figref{sf_crime}), 
and express her constraints and preferences in hope of a safer trip plan.
Note that in \figref{sf_crime} bad areas are the colored circles, whose
integer labels represent numbers of crimes in corresponding areas.

@@

\subsection{System Architecture}
\begin{figure*}[!ht]
  \centering
    \includegraphics[width=0.8\textwidth]{figs/system.pdf}
  \caption{System Overview\label{fig:system}}
\end{figure*}
We designed and implemented a multi-modal trip planning
system (cf. \figref{system}) based on a 
high-performance graph search engine.
The planner allows user uploads, as well as declarative
constraints and preferences.
We now describe the structure of the planning system.

@@

Our agent needs to travel without a car across San Francisco downtown at night.
For her, safety is important.
Having found the crime statistics for the area, the agent uploads
the data as a new auxiliary metric into the map.
By specifying that she will never walk through a neighborhood
with more than fifteen crimes over the last month, and that
she would sacrifice a quarter to avoid one crime incident,
the agent tells the planner to come up with a relatively safe
route. An example is shown in \figref{crime}, where the agent
needs to start at the east of downtown and travel across the area
to arrive at the west side.  
The computed path is represented by the line colored by black,
blue and green, denoting taxi, public transit and biking, respectively.
Clearly, this path routes away from crime-heavy areas and achieves
optimality in that the combined metrics -- time, fare and crime rates,
uploaded and personalized by the user -- is minimal among all possibilities.
